Smart Drill-Down

### 2015-07-09 TableSummarization/Paper/related.tex
changes to related work (and copy pasted intro changes

@@

\mrj{There has also been plenty of work on pattern mining. Several works~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} are non-interactive, and attempt to find a one shot summary of the table. This usually consumes a large amount of time processing the whole table, rather than allowing the user to slowly steer into portions of interest. In contrast, our work is interactive, and includes a smart memory manager that can use limited memory effectively while preparing for future requests.}

\mrj{Our Smart Drill-Down operator is tunable because of the flexible weighting function, but the monotonicity of the weighting function and the use of $MCount$, still make it possible for us to get an approximate optimality guarantee for the rules we display. In contrast, much of the existing pattern mining work~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117} is not not tunable enough, providing only a fixed set of interestingess parameters. On the other hand, reference~\cite{Leeuwen:2012:DSS:2347179.2347243} allows a fully general scoring function, necessitating the use of heuristics with no optimality guarantees, and very time consuming algorithms. 
A lot of pattern mining work~\cite{Goethals:2011:MFI:2020408.2020529,Yan:2005:SIP:1081870.1081907,Vreeken:2011:KMI:1969593.1969615} also focuses on itemsets rather than Relational Data, which doesn't allow the user to express interest in certain `columns' over others.}
% All the existing works solve a fixed optimization problem, whereas  we focus on finding an optimal summary for a flexible user-specified weighting function.

>>>>

% intro copy-paste for editing
%\mrj{Our work is also related to pattern mining. Several pattern mining papers~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} focus on providing one shot summaries of data, but do not propose interactive mechanisms. Moreover, to the best of our knowledge, other pattern mining work is either not flexible enough~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117}, restricting the amount of tuning the user can perform, or so general~\cite{Leeuwen:2012:DSS:2347179.2347243} as to preclude efficient optimization. Our work also merges `interesting pattern mining' into the OLAP framework. We discuss related work in detail in Section~\ref{sec:related}.}

@@

\mrj{There has also been plenty of work on pattern mining. Several works~\cite{Vreeken:2011:KMI:1969593.1969615,Bringmann:2007:ICDM,Yan:2005:SIP:1081870.1081907} propose non-interactive schemes that attempt to find a one shot summary of the table. These schemes usually consume a large amount of time processing the whole table, rather than allowing the user to slowly steer into portions of interest. In contrast, our work is interactive, and includes a smart memory manager that can use limited memory effectively while preparing for future requests.}

\mrj{Our Smart Drill-Down operator is tunable because of the flexible weighting function, but the monotonicity of the weighting function and the use of $MCount$, still make it possible for us to get an approximate optimality guarantee for the rules we display. In contrast, much of the existing pattern mining work~\cite{Goethals:2011:MFI:2020408.2020529,Tatti:2014:FRI:2676651.2656261,DeBie:2010:FMI:1816112.1816117} is not not tunable enough, providing only a fixed set of interestingess parameters. On the other hand, reference~\cite{Leeuwen:2012:DSS:2347179.2347243} allows a fully general scoring function, necessitating the use of heuristics with no optimality guarantees, and very time consuming algorithms. 
A lot of pattern mining work~\cite{Goethals:2011:MFI:2020408.2020529,Yan:2005:SIP:1081870.1081907,Vreeken:2011:KMI:1969593.1969615} also focuses on itemsets rather than Relational Data, which does not allow the user to express interest in certain `columns' over others.}
% All the existing works solve a fixed optimization problem, whereas  we focus on finding an optimal summary for a flexible user-specified weighting function.
